---
title: "Quiz12"
author: "b06208001 龔泓愷"
date: "2018年12月21日"
output: html_document
---
##Q426    
a. For short, the risk of having been bullied is 45.65217%.   
For not short, the risk of having been bullied is 25.64103%.    

```{r}
short = 92; short.bullied = 42; notshort = 117; notshort.bullied = 30

risk.short = short.bullied/short; risk.short
risk.notshort = notshort.bullied/notshort; risk.notshort
```

b. 1.780435   
The risk of short being bullied is 1.780435 times the risk for not short.    

```{r}
relative = risk.short/risk.notshort; relative
```


c. 78.04348%    
The interpretation of this percent increase in risk is that short students have a risk of being bullied is 78.04348% higher than the risk of not short students.    

```{r}
risk.increased = relative - 1; risk.increased
```

d. 2.436   
The odds of being bullied for short are 2.436 times the odds of not short.   
```{r}
short.unbullied = short - short.bullied; short.unbullied
notshort.unbullied = notshort - notshort.bullied; notshort.unbullied

odds.short = short.bullied/short.unbullied; odds.short
odds.notshort = notshort.bullied/notshort.unbullied; odds.notshort

odds.ratio = odds.short/odds.notshort; odds.ratio
```
