---
title: "Estimating Means with Confidence"
author: "b06208001 龔泓愷"
date: "2018年11月9日"
output: html_document
---
##Q1118
a. **0.2**    
The standard error of the mean of foot lenghs of women is smaller than thoe one of men because the sample size is **LARGER**.   
```{r}
n1 = 64; mu1 = 27.5; sd1 = 2
n2 = 100; mu2 = 24; sd2 = 2
se2 = sd2/sqrt(n2); se2
```

b. **0.3202**
```{r}
mud = mu1 - mu2;mud
sed = sqrt(sd1^2/n1 + sd2^2/n2);sed
```

##Q1132
Group1：Taking Zinc    
Group2：Taking Placebo
```{r}
n1 = 25;n2 = 23
mu1 = 4.5; mu2 = 8.1
sd1 = 1.6/sqrt(25); sd2 = 1.8/sqrt(23)
t <- qt((1 - 0.95)/2, df = 24, lower.tail = F);t
```
a. **[3.8396, 5.1604]**
```{r}
mu1 - t * sd1; mu1 + t * sd1
```

b. **[7.3254, 8.8746]** 
```{r}
mu2 - t * sd2; mu2 + t * sd2
```

c.
```{r}
plot(c(0,3),type='n',xlim=c(3,9),xlab='Mean Duration of Symptoms',ylab='',axes=F,
     main='Comparsion of the two confidence interval')

lines(c(3.8396,5.1604),c(2,2))
text(6.9,2,labels='Zinc')
lines(c(mu1 - t * sd1, mu1 - t * sd1),c(1.95,2.05))
lines(c(mu1, mu1),c(1.95,2.05))
lines(c(mu1 + t * sd1, mu1 + t * sd1),c(1.95,2.05))

lines(c(7.3254, 8.8746),c(1,1))
text(6.3,1,labels='Placebo')
lines(c(mu2 - t * sd2, mu2 - t * sd2),c(0.95,1.05))
lines(c(mu2, mu2),c(0.95,1.05))
lines(c(mu2 + t * sd2,mu2 + t * sd2),c(0.95,1.05))

axis(1)
```

##Q1150 
a. **[0.8172, 2.7828]**   
The interval tells us that we are of 95% confdence that the mean of difference ideal & actual heights of women aged 18~29 is between 0.8172 & 2.7828 inches.   
```{r}
n = 20;mu1 = 66.7; mu2 = 64.9; dbar = 1.8; sd = 2.1
se = sd/sqrt(20);se
t = qt((1 - 0.95)/2, df = 19, lower.tail = F)
CI.up = dbar + t * se; CI.up
CI.low = dbar - t* se; CI.low
```

b. Since the sample size is relatively small, it should meet condition1 for calculation in part(a)   

c. 'All women' in the sentence is wrong.    
It should be **on average**, women aged 18~29 would like to be taller.   

d. NO   
The condition on page428 is not appropriate for this condition, since it requires a larger sample size.   

##Q1160
a. Unpooled:**[-1.7274, 15.0607]**   
The data is approximately bell-shaped without skewness and outliers although the sample size isn't large enough.     
Therefore, computing the 95% confidence interval is justified.   
```{r}
Group1 <- c(72,84,66,72,62,84,76,60);n1 = 8;mu1 = mean(Group1);sd1 = sd(Group1)
Group2 <- c(62,72,60,63,75,64,60,52,64,80,68,64);n2 = 12;mu2 = mean(Group2);sd2 = sd(Group2)
t.test(Group1, Group2, alternative = 'two.sided', var.equal = F, paired = F, conf.level = 0.95)
```

b. Pooled:**[-1.1652, 14.4985]**
```{r}
sp = sqrt(((n1-1)*sd1^2 + (n2-1)*sd2^2)/(n1+n2-2));sp
se.pooled = sp*sqrt(1/n1 + 1/n2);se.pooled
df.pooled = n1 + n2 - 2;df.pooled
t <- qt((1-0.95)/2, df = df.pooled, lower.tail = F);t
CI.up = (mu1 - mu2) + t * se.pooled;CI.up
CI.low = (mu1 - mu2) - t * se.pooled;CI.low

#T-test var equal決定是不是pooled
t.test(Group1, Group2, alternative = 'two.sided', var.equal = T, paired = F, conf.level = 0.95)
```

c. Since the boudaries differ by about 0.6, we can easily notice that the two intervals are not very similar.     
The unpooled one is probably more accurate since the se.pooled is weighted average.   

##Q1178
a. **6.4106 seconds**
```{r}
n1 = 16;mu1 = 113.75;sd1 = 22.64#Alcohol
n2 = 16;mu2 = 99.87;sd2 = 12.04#Placebo
se = sqrt(sd1^2/n1 + sd2^2/n2);se
```

b. **[0.5852, 27.1748]**
```{r}
t <- qt((1-0.95)/2, df = 22, lower.tail = F);t
CI.up = (mu1 - mu2) + t * se;CI.up
CI.low = (mu1 - mu2) - t * se;CI.low
```

c. On the basis of part(b), we have 95% confidence to say that the populationmeans for the two groups are **different** since the intervals do not cover 0.   

d. It is reasonable to assume that both-populations are bell-shaped beacause most people take about the same amount of time to read out all the colours.       
Therefore, computing the 95% confidence is justified although the samplee size is not large enough.  

##Q1180
a. **Paired Data**
It is better to use paired data because two variables of interest are measured for each individual.   

b. A rnadom order is important because each individual might learn something in the first measurement and improve one's performance in the second measurement.   

c. **[-0.0402, 2.1735]**
```{r}
Dominant = c(22,19,18,17,15,16,16,20,17,15,17,17,14,20,26)
Undominant = c(18,15,13,16,17,16,14,16,20,15,17,17,16,18,25)
t.test(Dominant, Undominant, alternative = "two.sided", paired = T, var.equal = F, conf.level = 0.90)#paired = T成對資料與x = diff, y = NULL結果一樣
```

d. Since the intervals cover 0, we can not conclude whether dexterity is better for the dominant hand.    

##R Function Practice   
```{r}
Simd_CI <- function (n, mu1, mu2, sd1, sd2, m, conf.level){
  #成對樣本只需要一個n
  prob <- (1 - conf.level)/2#雙尾信賴區間
  t.value <- qt(prob, df = n - 1, lower.tail = F)#找T-Value
  
  dbar = c()
  se.d = c()
  mud = mu1 - mu2
  
  CI.half = c()
  CI.up = c()
  CI.lower = c()
  Check = c()#有沒有包含理論值的mud
  
  #取樣M次，每次n人
  for (i in 1:m) {
    x1 <- rnorm(n, mean = mu1, sd = sd1)
    x2 <- rnorm(n, mean = mu2, sd = sd2)
    dbar[i] <- mean(x1 - x2)
    se.d[i] <- sd(x1 - x2)/sqrt(n)
    
    #Calculate CIs
    CI.half[i] <- t.value * se.d[i]
    CI.up[i] <- dbar[i] + CI.half[i]
    CI.lower[i] <- dbar[i] - CI.half[i]
    
    if (CI.up[i] > mud & CI.lower[i] < mud){ 
      Check[i] <- 1 
    }else {
      Check[i] <- 0
    }
  }
  
  sd = sd(x1 - x2)#sqrt(var(x1) + var(x2)) #兩群體差的標準差
  
  plot(c(CI.up, CI.lower), type = 'n', #n是不畫圖，給空框架
       pch = 19, xlim = c(1, m), xlab = 'Trial',
       ylab = expression(dbar))
  
  abline(h = mud, col = 'blue')
  
  #Check whether each CI captures the mud
  for (i in 1:m){
    if (Check[i] == 1) {
      points(i, dbar[i], col = 'green', pch = 10)
      points(i, CI.up[i], col = 'green', pch = 20)
      points(i, CI.lower[i], col = 'green', pch = 20)
      lines(c(i, i), c(CI.lower[i], CI.up[i]), col = 'green', pch = 19)
    }else{
      points(i, dbar[i], col = 'red', pch = 10)
      points(i, CI.up[i], col = 'red', pch = 20)
      points(i, CI.lower[i], col = 'red', pch = 20)
      lines(c(i, i), c(CI.lower[i], CI.up[i]), col = 'red', pch = 19)
    }
  }
  
  title('Simulating Confidence Interval for mud')
  
  legend('bottomright', cex = 0.6, bty = 'n', ncol = 2,
         c('Captured', 'Not Captured'),
         fill = c('green', 'red'))
  
  NO.Captured <- m-sum(Check)
  RESULT <- list(Trial = m, Sample.Size = n,
                 Population.Differences.Mean = mud, 
                 Population.Differences.sd  = sd,
                 Confidence = conf.level,
                 NO.Captured = NO.Captured)
  
  return(RESULT)
}
Simd_CI(1000, 80, 90, 10, 5, 100, 0.95)
```

