---
title: "Estimating Proportions with Confidence"
author: "b06208001 龔泓愷"
date: "2018年11月2日"
output: html_document
---
##Q1012   
a. `margin of error = 0.98/sqrt(1100) = 0.0295 約= 0.03`
```{r}
high.c = 0.47 + 0.03;high.c
low.c = 0.47 - 0.03;low.c
```

**[0.44, 0.5]**   

b. The interval computed in part(a) means that we are 95% sure that the actual percentage of American adults who favor the legalization of marijuana is between 44% And 50%.   

##Q1022   
a. `p-hat = 0.3`    
b. `s.e. = sqrt(0.3 * 0.7 / 439) = 0.0219`    
c. `[0.3 - 1.96*0.0219, 0.3 + 1.96*0.0219]`   
**[0.257076, 0.342924]**    
d. The interval computed in part(c) means that we are 95% sure that the actual percentage of American teenagers who would rate their parents' strickness as 'less strict' compared to strictness of their friends' parents is betweeen 0.257076 & 0.342924.   

##Q1028   
a. `s.e. = sqrt(0.57 * 0.43 / 1006) = 0.0156`
`CI = [0.57 - 1.96 * 0.0156, 0.57 + 1.96 * 0.0156]`     
**[0.539424, 0.600576]**    

b. Yes.   
We are 95% confident that more than half of all Americans supported abortion only under certain circumstances.    
So, it is reasonable to infer that in 2009 the proportion of those was more than half.    

c. `s.e. = sqrt(0.18 * 0.82 / 1006) = 0.0121`   
`CI = [0.18 - 1.96 * 0.0121, 0.18 + 1.96 * 0.0121]`   
**[0.156284, 0.203716]**

##Q1048   
a. margin of error = 1/sqrt(n)    
`meargin of error = 1/sqrt(501) = 0.0477`   
About 4.47%, which they probably rounded off to 5%.   

b. [0.54 - 0.05, 0.54 + 0.05] = **[0.49, 0.59]**    
This means that we are 95% sure that the actual proportion of American teenagers said that they get along with their parents 'very well' is between 0.49 and 0.59.    

c. `2 * sqrt(0.54 * 0.46 / 501) = 0.0445`   
[0.54 - 0.0445, 0.54 + 0.0445] = **[0.4955, 0.5845]**     
The intervals are almost identical, just the one in part(c) seems a little narrower.     

d.
Conservative CI：[0.05 - 0.05, 0.05 + 0.05] = **[0, 0.1]**      
Precise CI：`2 * sqrt(0.05 * 0.95 / 501) = 0.0195`    
[0.05 - 0.0195, 0.05 + 0.0195] = **[0.0305, 0.0695]**   
The Precise CI is **much narrower** than the Conservative CI.   

e. Because the p-hat in part(b) which is 0.54 is **closer** to the conservative p-hat 0.5, there wasn't a big difference between precise one and the conservative one.       
On the other hand, the p-hat in part(d) which is 0.05 is further to the conservative p-hat, so the confidence intervals were not similar.   

##Q1054
a.    
```{r}
prop.test(x = c(85, 24), n = c(1105, 1379), alternative = 'two.sided', conf.level = 0.95)
```

**[0.04154, 0.07749]**    

b. The interval computed in part(a) means that we are 95% sure that the true proportion of snorers who have a heart disease is between 0.0415 & 0.0775 higher than non-snorers who have a heart disease.   
On the basis of that, we can infer that the population proportions with heart disease **differ** for snorers and non-snorers.   

##1066
a. Yes.   
It is reasonable to conclude that the population proportions experiencing sleep apnea differ for men and women since **the intervals do not overlap**.    

b. `p1-hat = (0.11 + 0.17)/2 = 0.14`    
`p2-hat = (0.04 + 0.08)/2 = 0.06`   
`p1-hat - p2-hat = 0.14 - 0.06 = 0.08`    
`s.e. = sqrt(0.14 * 0.86 / 524 + 0.06 * 0.94 / 542) = 0.0183`    
`[0.08 - 1.96 * 0.0183, 0.08 + 1.96 * 0.0183]` = **[0.044132, 0.115868]**   

c. The intereval we found in part(b) **does not include 0** which implies the two population proportions are **different**.   

## R Function Practice    
```{r}
Prop_CI_Diff <- function(n1, p1, n2, p2, confd){
  #Group1 Simu
  simu.phat1 = c()
  for (i in 1:10000) {
    phat = sum(sample(c(0,1), n1, replace = T, prob = c(1-p1,p1)))/n1
    simu.phat1[i] = phat
  }
  
  #Group2 Simu
  simu.phat2 = c()
  for (j in 1:10000) {
    phat = sum(sample(c(0,1), n2, replace = T, prob = c(1-p2,p2)))/n2
    simu.phat2[j] = phat
  }
  
  #Diff Phat
  diff.phat = simu.phat1 - simu.phat2
  diff.phat = sort(diff.phat)
  
  #
  low.per = ceiling(((1-confd)/2)*10000)
  low.vlue = diff.phat[low.per]
  high.per = ceiling((1-((1-confd)/2))*10000)
  high.vlue = diff.phat[high.per]
  
  results = c(paste((1-confd)/2*100,"%"), paste((1-((1-confd)/2))*100,"%"), low.vlue, high.vlue)
  
  mean.p = mean(diff.phat)
  sd.p = sd(diff.phat)
  
  CI = list(CI = matrix(results, nrow = 2, byrow = T), mean = mean.p, sd = sd.p, simu = diff.phat)
  
  return(CI)
}
```

###Ex10.10    
```{r}
#Simu
Prop_CI_Diff(1467, 0.624, 1575, 0.490, 0.95)[c('CI','mean', 'sd')]

#Calcu
n1 = 1467
p1 = 0.624
n2 = 1575
p2 = 0.490

mean = p1 - p2;mean
se = sqrt(p1*(1-p1)/n1 + p2*(1-p2)/n2);se
high.c = mean + 1.96 * se;high.c
low.c = mean -1.96 * se;low.c

#Hist
Prop_Diff <- as.numeric(as.character(unlist(Prop_CI_Diff(1467, 0.624, 1575, 0.490, 0.95)['simu'])))
hist(Prop_Diff, probability = T, breaks = 20,
   main = 'The Difference in Two Population proportions',
   xlab = 'The Difference in Two Population proportions',
   col = 'azure3', border = 'white')
abline(v = high.c)
abline(v = low.c)
```

可以看出模擬值與理論計算值十分接近。    
