---
title: "Random Variables"
author: "b06208001 龔泓愷"
date: "2018年10月5日"
output: html_document
---
####8.18
a. RR(X=0)、RL(X=1)、LR(X=1)、LL(X=2)     
b. P(RR) = 7/10 * 6/9 = 42/90    
P(RL) = 7/10 * 3/9 = 21/90     
P(LR) = 3/10 * 7/9 = 21/90    
P(LL) = 3/10 * 2/9 = 6/90     
c. P(X) = {X = 0 or 1 P(X) = 42/90, X = 2 P(X) = 6/90, X != 0, 1 or 2 P(X) = 0}   
d.
```{r warning = F}
Left_Handed <- c(0, 1, 2)
Probability <- c(42/90, 42/90, 6/90)
Q818 <- data.frame(Left_Handed, Probability)
library(ggplot2)
ggplot(Q818, aes(x = Left_Handed, y = Probability)) +
  geom_histogram(stat = 'identity')
```
<br>    

####8.40    
a. 
```{r}
0.2*20 + 0.8*15
```
b. No, it's not. It's never equal to the actual commute time for the expected value refers to the **long run average**.   

<br>    

####8.50
a. 
```{r}
choose(10, 5)*(1/2)^5*(1/2)^5
dbinom(5, size = 10, prob = 0.5)
```
b.
```{r}
choose(10, 7)*(1/2)^7*(1/2)^3
dbinom(7, size = 10, prob = 0.5)
```
c.
```{r}
choose(10, 7)*(1/2)^7*(1/2)^3 + choose(10, 8)*(1/2)^8*(1/2)^2 + choose(10, 9)*(1/2)^9*(1/2)^1 + choose(10, 10)*(1/2)^10*(1/2)^0
pbinom(6, size = 10, prob = 0.5, lower.tail = F)
```
<br>    

####8.72
mean = 500, sd = 100    
a. P(X<=500)，half of the population which its probability equals 0.5 
```{r}
a <- pnorm(500, mean = 500, sd = 100)
a
```
b. P(X<=650)    
```{r}
pnorm(650, mean = 500, sd = 100)
```
c.P(X>=700)
```{r}
c <- pnorm(700, mean = 500, sd = 100, lower.tail = F)
c
```
d.P(500<=X<=700)
```{r}
(1-c) - a
```
<br>    

####8.82
a. For a binomial distribution：   
mean = `np`   
sd = `sqrt(np(1-p))`    
```{r}
mean = 100 * 0.5
mean
sd = sqrt(100 * 0.5 * 0.5)
sd
```

b. P(>=60) by normal distribution approximation.    
```{r}
pnorm(60, mean = 50, sd = 5, lower.tail =  F)
```

c. P(>=59.5) by normal distribution approximation. 
```{r}
pnorm(59.5, mean = 50, sd = 5, lower.tail =  F)
```

d. P(>=60) by binomial function.    
```{r}
pbinom(59, size = 100, prob = 0.5, lower.tail = F)
```

e. For a binomial distribution, the most accurate value will be caculated by using `pbinom()`, which is (d.).   
On the other hand, the least accurate value will be caculated by using `pnorm()` without correction, which is (b.).   
<br>    

####8.90
a. Linear combinations of two normal distributions will be normal distribution as well.   
b. `mean(X-Y) = mean(X) - mean(Y) = 0`   
The mean supposed to be `0` if we did enough sampling.         
c. `variance(X-Y) = variance(X) + variance(Y)`    
`sd(X-Y) = sqrt(variance(X-Y)) = sqrt(variance(X) + variance(Y))`   
The sd should be`sqrt(2.8^2 + 2.8^2) = 3.96` if we did enough sampling.     
```{r}
#Setting
event = c()

for (i in 1:100000){

  sample <- rnorm(2, mean = 70, sd = 2.8)
  X = sample[1]
  Y = sample[2]
  D = X - Y
  
  event[i] = D
}
mean(event)
sd(event)
```
d. P(D > 3)   
```{r}
pnorm(3, mean = 0, sd = 3.96, lower.tail =  F)
```
e. P(D > 3| D <- 3)
```{r}
2*pnorm(3, mean = 0, sd = 3.96, lower.tail =  F)
```
<br>    

####Function Practice
* 某都市有10萬人口，某疾病每人每年感染機率為p = 0.01，請繪製該市每年感染人數頻率分布圖。     
```{r warning = F}
Population = c(1:100000)
Density = dbinom(Population, size = 100000, prob = 0.01)
Data <- data.frame(Population, Density)
ggplot(Data, aes(x = Population, y = Density)) +
  geom_line() +
  scale_x_log10() +
  ggtitle('每年感染人數頻率分布圖')
```

* 市長承諾，該年感染超過1050就下台。請問4年內市長下台機率。     
```{r warning = F}
d <- pbinom(1049, size = 100000, prob = 0.01, lower.tail = F) #P(>=1500) = 1- P(<=1049)每一年超過1050人得病的機率
pbinom(0, size = 4, prob = d, lower.tail = F)#P(>=1) = 1 - P(<=0) #至少一年有1050人以上
```

* 電腦模擬針對100年發生最大疫情規模的年度，估計該年度感染人數。     
```{r warning = F}
Disease <- function(n){
  #Setting
  disease.event = c()
  for(i in 1:n){ #模擬n年
    count = 0
    for (j in 1:100000){ #模擬10萬市民
      samp = sample(1:100, 1, replace = T)
      if (samp == 1){
        count = count + 1
      } 
    }
    disease.event[i] = count
  }
  return(disease.event)
}
max(Disease(100))
```