---
title: "Random Variables"
author: "b06208001 龔泓愷"
date: "2018年10月5日"
output: html_document
---
####8.18
<br>    

####8.40
<br>    

####8.50
<br>    

####8.72
<br>    

####8.82
a. For a binomial distribution：   
mean = np   
sd = sqrt(np(1-p))    
```{r}
mean = 100 * 0.5
mean
sd = sqrt(100 * 0.5 * 0.5)
sd
```

b. P(>=60) by normal distribution approximation.    
```{r}
pnorm(60, mean = 50, sd = 5, lower.tail =  F)
```

c. P(>=59.5) by normal distribution approximation. 
```{r}
pnorm(59.5, mean = 50, sd = 5, lower.tail =  F)
```

d. P(>=60) by binomial function.    
```{r}
pbinom(59, size = 100, prob = 0.5, lower.tail = F)
```

e. For a binomial distribution, the most accurate value will be caculated by using `pbinom()`, which is (d.).   
On the other hand, the least accurate value will be caculated by using `pnorm()` without correction, which is (b.).   
<br>    

####8.90
a. Linear combinations of two normal distributions will be normal distribution as well.   
b. `mean(X-Y) = mean(X) - mean(Y) = 0`   
The mean supposed to be `0` if we did enough sampling.         
c. `variance(X-Y) = variance(X) + variance(Y)`    
`sd(X-Y) = sqrt(variance(X-Y)) = sqrt(variance(X) + variance(Y))`   
The sd should be`sqrt(2.8^2 + 2.8^2) = 3.96` if we did enough sampling.     
```{r}
#Setting
event = c()

for (i in 1:100000){

  sample <- rnorm(2, mean = 70, sd = 2.8)
  X = sample[1]
  Y = sample[2]
  D = X - Y
  
  event[i] = D
}
mean(event)
sd(event)
```
d. P(D > 3)   
```{r}
pnorm(3, mean = 0, sd = 3.96, lower.tail =  F)
```
e. P(D > 3| D <- 3)
```{r}

```
<br>    

####Function Practice